%*
%* Seven Kingdoms: Ancient Adversaries
%*
%* Copyright 1997,1998 Enlight Software Ltd.
%* Copyright 2018 Timothy Rink
%*
%* This program is free software: you can redistribute it and/or modify
%* it under the terms of the GNU General Public License as published by
%* the Free Software Foundation, either version 2 of the License, or
%* (at your option) any later version.
%*
%* This program is distributed in the hope that it will be useful,
%* but WITHOUT ANY WARRANTY; without even the implied warranty of
%* MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
%* GNU General Public License for more details.
%*
%* You should have received a copy of the GNU General Public License
%* along with this program.  If not, see <http://www.gnu.org/licenses/>.
%*
%*

\chapter[Fire and the Forces of Nature]{{\Huge F}IRE AND THE {\Huge F}ORCES OF {\Huge N}ATURE}

\section{\textsf{Fire}}

\index{fire}

\textswab{\huge{F}}ires, which can be started by lightning, weapons fire, or the wrath of certain Greater Beings, will usually burn for a short while before they go out by themselves. Although they will not spread, there is no action that you can take that will put them out apart from Invoking Thor to bring rain. The length of time that a fire burns will depend on the terrain type and on the weather.

Fires may be put out by Rain or Snow.

If you wish to keep a fire burning, you must help it along with, for instance, Naphtha projectiles from your Catapults.

The effects of fire are many. In a Village, it will kill the people. In a building, it will damage the structure. It will damage all mobile units that it comes in contact with it, and it will destroy trees and other plants.

\section{\textsf{Lightning}}

\index{lightning}

% Condensed sentences here.

\textswab{\huge{L}}ightning is a random event. Unless called down by Thor, it will only cause damage when the Random Event Option is enabled. Lightning can strike and cause damage to units, structures, Villages, and plants.

\section{\textsf{Earthquakes}}

\index{earthquakes}

\textswab{\huge{E}}arthquakes are random events. They will only cause damage when the Random Event Option is enabled.

Earthquakes will damage buildings and may damage units that are in Villages as well. Units inside of buildings will be safe from Earthquakes.

\section{\textsf{Rain}}

\index{rain}

\textswab{\huge{R}}ain will cause no damage, but it will slow down the movement speed of mobile units. Rain will also extinguish fires.

\section{\textsf{Snow}}

\index{snow}

\textswab{\huge{S}}now, like rain, will cause no damage. It will slow down the movement speed of mobile units. Snow can also extinguish fires.

\section{\textsf{Tornadoes}}

\index{tornados}

\textswab{\huge{T}}ornadoes are random events. Unless they are summoned by Thor, they will only appear when the Random Event Option is enabled.