%*
%* Seven Kingdoms: Ancient Adversaries
%*
%* Copyright 1997,1998 Enlight Software Ltd.
%* Copyright 2018 Timothy Rink
%*
%* This program is free software: you can redistribute it and/or modify
%* it under the terms of the GNU General Public License as published by
%* the Free Software Foundation, either version 2 of the License, or
%* (at your option) any later version.
%*
%* This program is distributed in the hope that it will be useful,
%* but WITHOUT ANY WARRANTY; without even the implied warranty of
%* MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
%* GNU General Public License for more details.
%*
%* You should have received a copy of the GNU General Public License
%* along with this program.  If not, see <http://www.gnu.org/licenses/>.
%*
%*

\chapter[Introduction]{{\Huge I}NTRODUCTION}

\textswab{\huge{E}}nter the world of \textit{Seven Kingdoms: Ancient Adversaries}, a world of intrigue and diplomacy, of trade, conquest, and espionage.

% typo here

Take control of any of the following emerging civilizations: Chinese, Persian, Japanese, Greek, Norman, Viking, Mayan, Egyptian, Mughul, or Zulu.

Begin with a single, modest village under your command, and go on to conquer an entire world by force of arms, by guile and persuasion, or by whatever other means you choose.

\textit{Seven Kingdoms: Ancient Adversaries} is a real-time game of epic strategy and empire building. Players compete against up to six AI opponents or human players for control of land, trade, and peoples.

Wage open warfare on your rivals, or forge alliances with them. Send spies to infiltrate their ranks, or hold your spies back to guard against your enemies’ prying eyes. Mine ore and manufacture goods, then build markets and establish trade routes to bring gold flowing into your coffers. Have your scientists research new weapons of war, or turn from science to the mystic arts, and seek the ultimate power: the ability to summon the aid of the gods. All these choices and more are yours.